Body Image and Trikafta

### 2023-03-10 Emily Muther/body_image_trikafta.qmd
started body image trikafta over

---
title: "Body Image and Trikafta"
author: "Tim Vigers"
date: "`r format(Sys.time(), '%d %B %Y')`"
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
editor: visual
---

```{r}
#| include: false
# Libraries
library(haven)
library(tidyverse)
library(arsenal)
# Import
df = read_sav("Z:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Body Image and Trikafta/Data_Raw/TrikaftaBodyImage1.11.23.sav")
# Format variables
df$`Percent Adherence` = factor(df$PercentAdherence,levels = 1:11,
                             labels = paste0(seq(0,100,by=10),"%"),ordered = T)
df$`FRS Category` = factor(df$FRS_Category,levels = -1:1,
                           labels = c("want to be larger","neutral",
                                      "want to be smaller"))
df$`Doses Missed` = as.numeric(df$DosesMissed)
df$`Weight/Body Adherence` = factor(df$WeightBody_Adherence,levels = 1:5,
               labels = c("Strongly Agree","Slightly Agree","Neutral",
                          "Slightly Disagree","Strongly Disagree"))
df$`Weight/Body Adherence` = fct_rev(df$`Weight/Body Adherence`)
df$`Weight/Body Adherence` = factor(df$`Weight/Body Adherence`,ordered = T)
```

Because we want to keep the ordinal nature of some of these variables rather than simply treating them as categorical (i.e. with percent adherence it's meaningful that 10% \< 20% \< 30% ...), Emma is right in thinking that ordinal logistic regression is the right approach. Unfortunately, this requires estimating a lot of parameters, and we probably don't have the necessary numbers for it (for example, with percent adherence as the outcome we'd need to estimate 12 parameters, and the general rule of thumb is at least 10 observations per parameter).

So, after talking this through with another statistician in our group, I think the best way to approach this is to treat these variables as continuous, but apply non-parametric, rank-based tests between various groups. This keeps the information about the order of the categories but does not assume normal distribution, etc.

```{r results='asis'}
#| label: tbl-1
#| tbl-cap: Comparisons by FRS Category
t1 = tableby(`FRS Category`~kwt(`Percent Adherence`)+`Doses Missed` +
               kwt(`Weight/Body Adherence`),data = df,
             control=tableby.control(numeric.stats=c("Nmiss","median","q1q3","range"),
                                     numeric.test="kwt"))
summary(t1,pfootnote = T)
```

```{r}
#| label: fig-planets
#| fig-cap: Planets

@@

# Questions

1. Which variables should be considered ordinal and which categorical?

>>>>

---
title: "Body Image and Trikafta"
author: "Tim Vigers"
date: today
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
editor: visual
---

```{python}
# | include: false
import pandas as pd
# Read in data
df = pd.read_spss(
    "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Body Image and Trikafta/Data_Raw/TrikaftaBodyImage3.6.23.sav")
```

# Data Cleaning Steps

1. Participants who answered "I don't know" or "no" on the variable `TakingTrikafta` were excluded from these analyses.

```{python}
# | include: false
# | eval: false
from ydata_profiling import ProfileReport
# EDA
profile = ProfileReport(df, explorative=True)
# Saving results to a HTML file
profile.to_file(
    "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Body Image and Trikafta/Reports/eda.html")
```

```{python}
# Filter
df = df[df["TakingTrikafta"] == "yes"]
```

```{python}
# | label: tbl-planets
# | tbl-cap: Planets

@@

# Figure

```{python}
# | label: fig-planets
# | fig-cap: Planets
